Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-15 paper/main.tex
graphs

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

@@

PLOT Type: Bar Graph (with multiple bars)

PLOT Y Axis: Model Accuracy

PLOT X Axis: Top-1, Top-2, Top3

PLOT Bars: 1 for our algorithm, 1 for a weak baseline (such as the vanilla
Python interpreter)

@@

Ranjit: ``our algorithms'' --- ``purely syntactic vs. with types''
--- ``with or without slicing'' as extra ``bars''

@@

@@

PLOT Type: Table

TABLE COLUMNS: Feature Name, Feature Category, Feature Predictive Power

TABLE ROWS: top twelve features

@@

TODO: do ANOVA or ReliefF

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{pgfplots}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={Top-1,Top-3},
    xtick=data,
    ymin=0,
    ylabel=Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=withEverything, col sep=comma]{fault-localization.csv};
    \addplot table[x=scoreName, y=baseline, col sep=comma]{fault-localization.csv};
\legend{Our best model,Python interpreter}
\end{axis}
\end{tikzpicture}
\caption{Based on a decision tree on the largest
dataset (272534 pairs). TODO: also train for Top-2}
\label{fig:full-dataset-acc}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={Top-1,Top-3},
    xtick=data,
    ymin=0,
    ylabel=Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=all, col sep=comma]{removing-features.csv};
    \addplot table[x=scoreName, y=noTypes, col sep=comma]{removing-features.csv};
    \addplot table[x=scoreName, y=noContext, col sep=comma]{removing-features.csv};
    \addplot table[x=scoreName, y=noSlice, col sep=comma]{removing-features.csv};
\legend{All Features,No Types, No Context, No Slicing}
\end{axis}
\end{tikzpicture}
\caption{Accuracy when features are removed, based on decision trees on a random subset of 20000 pairs.
TODO: train better model and/or
train on greater fraction of the data? TODO: Top-2. NOTE: removing slicing makes basically no difference...}
\label{fig:removing-features}
\end{figure}

@@

@@

PLOT: See Figs. \ref{fig:full-dataset-acc} and \ref{fig:removing-features}

@@

\begin{table}[]
\begin{tabular}{l|l|l}
Feature Name & Feature Category & Feature Predictive Power \\ \hline
F-Type-C1=unknown & Contextual (Type) & 0.112 \\
F-Type-P=TUPLE & Contextual (Type) & 0.108 \\
F-Stmt-Constr-C2=Return & Contextual (Syntactic) & 0.068 \\
F-Expr-Constr=Paren & Syntactic & 0.059 \\
F-InSlice=0.0 & Slicing & 0.044 \\
F-Type-P=str & Contextual (Type) & 0.036 \\
F-Op-Contr-C3=BinaryAnd & Contextual (Syntactic) & 0.026 \\
F-Type-C2= & Contextual (Type) & 0.025 \\
F-Type-C1=str & Contextual (Type) & 0.023 \\
F-Type-P=float & Contextual (Type) & 0.019 \\
\end{tabular}
\caption{Based on the Top-1 Decision Tree on the full dataset. Feature Predictive Power here is the Gini Importance. TODO: add
better-known measure like ANOVA or ReliefF. TODO: add a couple more features?}
\label{tab:feature-predictive-power}
\end{table}

@@

PLOT: See Table \ref{tab:feature-predictive-power}

@@
